Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-10-31 doc/paper.tex
equiring the agent to find specific keys scattered throughout the environment. These keys serve as the ticket to unlock doors, enabling progress to new areas and ultimately leading to the completion of the task at hand...
Signed-off-by: Gregz9 <gregorkajda@gmail.com>

>>>>

Many research papers nowadays propose fine-tuning of LLMs as means of leveraging the capabilites of the language models for decision-making purposes even further. Our plan of action, on the other hand, aims at evaluating the efficacy of the LLM without any previous pre-tuning. From the perspective of reinforcement learning, is is the appropriate course of action, as the LLM should not possess any previous knowledge about the task at hand, just like the agent should not. In addtion, the act of fine-tuning LLM is a rather time-comsuming process, requiring the generation and structuring of a new dataset, and also vast hardware resources.
